Master's Project Journal

### 2019-04-09 thesis/Background.tex

\end{quotation}
By carrying out simulations on an \ac{FPGA}, Guanhua Wang \textit{et al} (2013) achieved a 3000 times decrease in run-time when compared to an identical simulation in MATLAB used for the verification of a calibration algorithm for successive approximation analog-to-digital converters \cite{wang2013fast}. Many other examples exist of \ac{FPGA}s used for the simulation of mixed-signal or \acl{RF} circuits in literature.
%TODO Elena had suggestions?

>>>>

\end{quotation}
By carrying out simulations on an \ac{FPGA}, Guanhua Wang \textit{et al} (2013) achieved a 3000 times decrease in run-time when compared to an identical simulation in MATLAB used for the verification of a calibration algorithm for successive approximation analogue-to-digital converters \cite{wang2013fast}. Many other examples exist of \ac{FPGA}s used for the simulation of mixed-signal or \acl{RF} circuits in literature.
%TODO Elena had suggestions?

\section{\ac{ADPLL} Performance Characterisation}
As already stated, goal of a clock distribution system is to synchronise clocking events in all areas of the chip. The effectiveness of this synchronisation is characterised by two main metrics, jitter and skew, which together describe the distribution of clocking events. Skew is the average time delay between a clocking event in one area of the chip and that of a reference event. It can be easily measured by computing the average value of this delay. Jitter has a number of definitions depending on how it is measured, but at its most basic it is the standard deviation of the time delays with respect to the reference clocking edge.

The simplest form of clock performance characterisation is on a \ac{C2C} basis, in which the reference is the signal under test itself. Here the standard deviation of the individual periods gives the jitter of the signal, while skew has no meaning with a self reference the mean period can be used to compute the centre frequency over the time interval. For a more informative measurement the \ac{TIE} can be computed, which takes into account another signal as the reference. \ac{TIE} is calculated by comparing the delay between the signal in question and a reference that is treated as ideal. The mean value gives the relative skew between the two signals and once more the standard deviation of the measurements gives the jitter with respect to this reference.

Both above forms of measurement assume a large number of sequential measurements, however, there are other ways that jitter and skew can be calculated \cite{sadsadad}. Phase jitter is an important characteristic for communications systems as it can be used to calculate phase noise, important to ensure spurious emissions are within regulations. Long term, or accumulated, jitter represents the cumulative effect of jitter on the signal over several cycles. Long term jitter in particular affects \acs{RADAR} as it will manifest itself as a Doppler shift in the return signal. For an \ac{PLL} network, with an appropriately designed filter, the long term jitter should be zero so long as the reference signal is stable. %TODO ask Brian about this one
